Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
paper updated

\section{Introduction}
Looking at the field of artificial neuronal networks (NN), one finds a great
variety of different models describing both the dynamic of networks as well
as their plasticities, i.e.\ their learning behavior. 
But, given some dynamics and plasticity rules, which features of a network
determine whether it is a good candidate for doing a specific task?
%But what exactly makes artificial neuronal networks learn successfully? And
%why are certain types of networks and certain learning rules effective for
%some problems, but fail at solving others? 
%Confronting and eventually
%answering these questions is critical when trying to gain a deep
%understanding of neural networks and artificial intelligence.

@@

Using this question as a guideline, we decided to analyze which high level
properties of a NN are important for its learning success under a variant
of the FORCE algorithm \citep[Architecture A]{FORCE}, and how to choose
their values for an optimal result.

%To this end, one option would be to take an
%initial network and an adequate periodic pattern to be learned, and
%optimize the network's internals for this very task. Then patterns may
%emerge that hint at how an optimal network design looks. 
%However, we took a different approach:
Instead of fine tuning single internal weights, we were thus concerned with the
general rules of the network's properties. And we wanted our networks to
be random to a certain degree, which seems biologically plausible; but we
also wanted to allow for structural specialization:
How densely are the synapses distributed? How strong shall the feedback
signal be, and how strong should the synapses fire on average?
%To address these issues we looked at parameterized random networks (in
%the language of genetics, as we are using a genetic optimization algorithm, at different 
%\emph{network genotypes}).

@@

\section{Concepts and Model}
\label{sec:concepts}
\paragraph{Network Model} 
%MAYBE WE SHOULD MOTIVATE FORCE HERE, WHICH THEN NATURALLY LEADS TO THE CHOICE OF NETWORK BELOW.

We chose the same rate based network architecture
that is used in the original FORCE publication \citep{FORCE} (therein denoted as
architecture A) and also in \citep{RM}, where our notation mainly stems
from. So we look at a network $\mathcal{N}$ with $N$ internal neurons and
states $x_i$ for $1 \le i \le N$ that loosely represent the neurons'
membrane potential. The firing rate $r_i$ of the $i$-th internal neuron is
given by $r_i = \tanh x_i$.  Furthermore, the network contains $R$ readout
neurons with states $z_i$ for $1 \le i \le R$, where
\begin{equation} 
    z_i = \sum_{j=1}^{N}\omega\Ix{read}_{ij}\,r_j
\end{equation}
with the readout weights $\omega\Ix{read}$.
Taking into account both internal dynamics as well as an external feedback
pathway, the dynamics $t \mapsto x_i(t)$ of the single neurons are governed
by \footnote{~Note that we did not include external input signals in this
formula, as is done in \citep{FORCE} and \citep{RM}.}
\begin{equation}
    \dot{x}_i(t) = -x_i(t) + \sum_{i=1}^N \omega\Ix{rec}_{ij}\, r_j(t) + 
                   \sum_{i=1}^R \omega\Ix{fb}_{ij}\, z_j(t)~,
\end{equation}
where we introduce the internal recurrent synapse weights
$\omega\Ix{rec}_{ij}$ and the feedback synapse weights
$\omega\Ix{fb}_{ij}$. 
We solved this system of differential equations by
Euler integration with a time steps $dt = 0.01$, which was
also used in \citep{FORCE}. 
%(How we constructed $\omega\Ix{rec}$ and
%$\omega\Ix{fb}$ will be described in \emph{Parametric Random Networks})

\paragraph{Learning} Learning took place by stepwisely adapting the weights
$\omega\Ix{read}$ so that the dynamics $t\mapsto r_i(t)$ of the readout
neurons should eventually match a given periodic target pattern $t\mapsto
r'_i(t)$, henceforth called a \emph{task}, as accurately as possible. To
update $\omega\Ix{read}$ we chose variant A of the FORCE algorithm
\citep{FORCE}, which rapidly modifies the feedback loop to keep the errors
$|r_i(t) - r'_i(t)|$ small from the beginning on.

@@

\paragraph{Network Genotypes} Since we are not
interested in single network properties, but rather want to find out which
structural elements of networks are important for learning success, we
introduced  \emph{network genotypes}.
Such a genotype $G$ consists of a set $\Theta$ of parameters that determine
which concrete networks are created when $G$ is expressed in a single
phenotype. Technically $G$ may be understood as a stochastic network
generator that returns a network $\mathcal{N}=G(\lambda)$ for every seed
$\lambda \in \mathbb{N}$.
The genotypes' parameters $\theta\in\Theta$ are either integer or floating
point values and can be classified as affecting either (1) the topology of
$\omega\Ix{rec}$ or (2) the weight values of $\omega\Ix{rec}$ and
$\omega\Ix{fb}$. Important examples for (1) are the networks size $N$, the
occupation probability $p$ (for random Erdös-Renyi networks), and the
neighborhood range $k$ (for ring topologies). We furthermore introduced ratio parameters $r$
that allowed us to interpolate between different topologies. Optimized
parameters of type (2) were the feedback strength $\feedback$ (with
$\omega\Ix{fb}\propto \feedback$) and the gain value $\gain$ (with
$\omega\Ix{rec} \propto \gain$).

\paragraph{Fitness} The next step was to define the \emph{fitness} of a given
genotype when confronted with a diverse range of tasks, e.g. waves of
different frequencies. To express this formally, we introduced
\emph{challenges}: For a given seed value $\lambda$, the challenge $C$
yields a task $r' = C(\lambda)$ according to some (parametrized)
distribution. If we now make use of a success function $S(\mathcal{N},
r')\in\{0, 1\}$ that decides whether the NN $\mathcal{N}$
has successfully reproduced the desired output $r'$, the fitness $F_C(G)$
of a genotype $G$ for a challenge $C$ may reasonably be defined as the
expectation value of $\lambda \mapsto S(G(\lambda), C(\lambda))$. For fixed
challenges, the main task of optimizing the genotype is now reduced to
finding parameters $\Theta$ that maximize $F_C$.

% IDEA: Maybe put this part at the end of the paper. Most things needed to
% understand the results (in principle) have already been mentioned at this
% point.
\section{Methods and Implementation}
\label{sec:implementation}

\paragraph{Tasks}
For the optimization to work properly, the tasks presented to the networks
must be chosen reasonably; they must be learnable by FORCE (at least in
principle) and must be compatible with technical aspects like the
integration time step. 
%While it was shown in \citep{FORCE} that large recurrent neural networks are
%capable of learning very complex tasks, the optimization requires an
%extensive number of learning processes, since every single evaluation of
%the fitness $F_C$ needs dozens of tested phenotypes (see below). Therefore,
%the networks had to be restricted to being quite small ($\approx 100$
%neurons) and are consequently less powerful.

To get a first estimate whether it might be possible to learn a given task
using FORCE with 100 neurons in our network model, we looked at a single
sinusoidal of frequency $\omega$ and determined the frequency range in
which an (unoptimized) network (i.e. \gain, \feedback, \ERprob) is able to
learn the function (see fig. \ref{}).

Since we expect/hope that the optimized network extends this range of
possible frequencies, we choose the frequencies for the optimization tasks
from the slightly larger interval $[\num{0.6e-2}, 4]$ such that their logarithms
% TODO this number is no longer right: we have low, high and full
are uniformly spaced. This allows for good resolution for both high and low
frequencies.

\paragraph{Success}
As mentioned in \emph{Concepts and Methods}, we need a function $S$
that decides whether a network succeeded or failed to solve a task.
To this end
%In order to optimize the function reconstruction of a force network,
a measure $f(r', r)$ for the concordance of the target function $r'(t)$ and
the network readout $r(t)$ is sought. Though one could use a simple
difference based metric, like the norm $f\ix{2}(r, r')
= \left\|r-r'\right\|_2$, this has the drawback that small phase
mismatches could produce high differences, even though the
shape of $r$ matches the one of $r'$ well.

A measure that is time-shift independent and maximized for functions of
identical shape is the maximum of the cross correlation 
\begin{align}
    f\ix{cor}(r, r') = \max_t \frac{\left<r, r'(\cdot
    - t)\right>}{\sqrt{\left< r, r\right> \left<r', r' \right>}}~.
\end{align}
Algorithmically, the signals $r$ and $r'$ are split into overlapping chunks
which are correlated separately.  This saves computational power and
prevents minute differences in frequency to accumulate into a huge phase
shift, so the phase only has to remain relatively constant over the
timescale of a single chunk (which is about 10 seconds of simulated time).
%This measure becomes problematic for functions that are very close to zero
%for a longer time (order of chunk size), but since we are going to work
%with superpositions of sinusoidals, this drawback
%is unproblematic.

Using this measure of quality, the success function for a network
$\mathcal{N}$ with readout $r$ for the task $r'$ was taken to be 
\begin{equation}
    S(\mathcal{N}, r') = \begin{cases} 1\quad\mathrm{if}~f\ix{cor}(r, r') \ge 0.95,\\
                                       0\quad\mathrm{if}~f\ix{cor}(r, r') < 0.95~.
                         \end{cases}
\end{equation}
The threshold value of 0.95 was determined empirically, as signals $r$ with
$f(r, r') \ge 0.95$ met our assessment of what we considered a good
reproduction of the target pattern.

\paragraph{Genetic Optimization}
Due to the stochastic nature of a genotype $G$'s fitness $F_C(G)$,
a very high number of samples would be required to numerically obtain sufficiently
smooth approximations of $F_C(G)$ for typical optimization methods like
gradient descend or simulated annealing. But as the computational cost for
even one learning process is considerable high, these methods were not
feasible.

@@

Therefore, we optimized $F_C(G)$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le N\right\}$
of $N$ individuals (Generators) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}[itemsep=1ex, leftmargin=0pt]
 \item[Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 50 samples (and adaptively more if the
     $(F_i)_{1\le i\le N}$ are spaced closely, to at most 100).
 \item[Selection] We choose $p=50\%$ of the most successful members of $G_t$ as survivors.
With a small chance, a weaker generator can survive, in order to keep the gene pool more diverse.

\item[Reproduction] We then replace the $(1-p)|G_t|$ elements that did not make
it into the next generation by either \emph{mutating} or \emph{recombining} the 
survivors and get $\mathcal{G}_{t+1}$. This means we either change
    a single parameter randomly or take two individuals and randomly choose
    for each parameter from which parent to take the value.   
\end{description}

\paragraph{Choice of Parameters and Algorithmic Quantities}
The mutation rate of the parameters $\Theta$ of the genotypes\dots

@@

The most striking result is the strong growth of the feedback for
$C\ix{high}$ to values higher than 14, while the value for $C\ix{low}$
converges quickly to approximately 1 (FIG. \ref{fig:freq_optimization} (b)).
This behavior may indicate that the feedback pathway must
overshadow the (maybe too slow) internal mechanics for high frequencies,
while it is the other way round for low frequencies.
Indeed, FIG. \ref{fig:freq_optimization} (a) shows that genotypes with
a lower gain value (on average) are more successful for high frequencies,
which seems to fit in: excessive recurrent dynamics with a long time
scale (compared to the period to be learned) may disturb the learning.
That the single genotypes remain quite scattered throughout the whole
optimization process, though, implies that the exact gain value is not
critical for the success of a genotype.

@@

But how well did the fitness actually improve during the optimization?
When looking at FIG. \ref{fig:freq_optimization} (d), one sees that the
fitness for $C\ix{high}$ increased during nearly the whole process, while
the algorithm failed to further optimize the genotypes' fitness for
$C\ix{low}$ after about 20 generations. A major reason for this is
probably, that the initial population for the $C\ix{low}$ optimization
already contained genotypes with parameters similar to the (at least
locally) optimal ones.

@@

\section{Discussion}
- Remarks
    * Influence of initial conditions
        -> Degenerated initial population poses major problems (does not
        find same / takes very long to find same parameters as when started
        with diversity).
        -> With broad diversity: often fast convergence -> Gen. Optimizer
        good as optimizing filter, but has hard times to explore new
        parameter regions if no right genotypes are present (especially isolated
        maxima of $F_C$). Solution: Could introduce migrants, that supply
        the gene-pool with underrepresented genotypes.
    * According to experience: maybe not ideal for finding single set of
      parameters but rather for successful parameter-ranges (branches?)

- Problems
    * Only few and uncomprehensive number of test / experiments conducted due to the
      computational cost.
    * Influence of statistics: Learning success depends stronger on choice
      of challenges than parameters (partially) -> must be very careful how to
      interpret the results / should have used fixed array of challenges instead
      of random sampling

>>>>

\section{Introduction}
Looking at the field of artificial neuronal networks, one finds a great
variety of different models describing both the dynamic of networks as well
as their plasticities, i.e.\ their learning behavior. 
But, given some dynamics and plasticity rules, which features of a network
determine whether it is a good candidate for doing a specific task?
%But what exactly makes artificial neuronal networks learn successfully? And
%why are certain types of networks and certain learning rules effective for
%some problems, but fail at solving others? 
%Confronting and eventually
%answering these questions is critical when trying to gain a deep
%understanding of neural networks and artificial intelligence.

@@

Using this question as a guideline, we decided to analyze which high level
properties of a neuronal network are important for its learning success
under a variant of the FORCE algorithm \citep[Architecture A]{FORCE}, and
how to choose their values for an optimal result.

%To this end, one option would be to take an
%initial network and an adequate periodic pattern to be learned, and
%optimize the network's internals for this very task. Then patterns may
%emerge that hint at how an optimal network design looks. 
%However, we took a different approach:
Instead of fine tuning every single internal weight, we were thus concerned
with the general rules of the network's properties. And we wanted our
networks to be random to a certain degree, which seems biologically
plausible; but we also wanted to allow for structural specialization: How
densely are the synapses distributed? How strong shall the feedback signal
be, and how strong should the synapses fire on average?
%To address these issues we looked at parameterized random networks (in
%the language of genetics, as we are using a genetic optimization algorithm, at different 
%\emph{network genotypes}).

@@

\section{Concepts and Model}
\label{sec:concepts}
\paragraph{Network Model}

We chose the same rate based network architecture that is used in the
original FORCE publication \citep{FORCE} (therein denoted as architecture
A) and also in \citep{RM}, where our notation mainly stems from. So we look
at a network $\mathcal{N}$ with $N$ internal neurons and states $x_i$ for
$1 \le i \le N$ that loosely represent the neurons' membrane potential. The
firing rate $r_i$ of the $i$-th internal neuron is given by $r_i = \tanh
x_i$.  Furthermore, the network contains a readout neuron with the state
\begin{equation} 
z = \sum_{j=1}^{N}\omega\Ix{read}_{j}\,r_j
\end{equation}
where $\omega\Ix{read}$ denotes the readout weight vector.
Taking into account both internal dynamics as well as an external feedback
pathway, the dynamics $t \mapsto x_i(t)$ of the single neurons are governed
by \footnote{~Note that we did not include external input signals in this
formula, as is done in \citep{FORCE} and \citep{RM}.}
\begin{equation}
    \dot{x}_i(t) = -x_i(t) + \sum_{i=1}^N \omega\Ix{rec}_{ij}\, r_j(t) + 
                   \sum_{i=1}^R \omega\Ix{fb}_{ij}\, z_j(t)~,
\end{equation}
where we introduce the internal recurrent synapse weights
$\omega\Ix{rec}$ and the feedback synapse weights
$\omega\Ix{fb}$. 
We solved this system of differential equations by
Euler integration with a time steps $\mathrm{d}t = 0.01$, which was
also used in \citep{FORCE}. 
%(How we constructed $\omega\Ix{rec}$ and
%$\omega\Ix{fb}$ will be described in \emph{Parametric Random Networks})

\paragraph{Learning} Learning took place by stepwisely adapting the weights
$\omega\Ix{read}$ in such a way that the readout dynamic $t\mapsto z(t)$
should eventually match a periodic target pattern $t\mapsto
z'(t)$, henceforth called a \emph{task}, as accurately as possible. To
update $\omega\Ix{read}$ we chose variant A of the FORCE algorithm
\citep{FORCE}, which rapidly modifies the feedback loop to keep the errors
$|z(t) - z'(t)|$ small from the beginning on.

@@

\paragraph{Network Genotypes} 
In order to find out which structural elements of networks are important
for learning sucess, we introduce \emph{network genotypes}.
%Since we are not interested in single network
%properties, but rather want to find out which structural elements of
%networks are important for learning success, we introduced  \emph{network
%genotypes}.
%Such a genotype $G$ consists of a set $\Theta$ of parameters that determine
%which concrete networks are created when $G$ is expressed in a single
%phenotype. 
Technically, a genotype $G$ with parameters $\Theta$ may be understood as
a stochastic network generator that returns a network
$\mathcal{N}=G(\lambda)$ for every seed value $\lambda$.

The genotypes' parameters $\theta\in\Theta$ are either integer or floating
point values and can be classified as affecting (1) the topology of
$\omega\Ix{rec}$ or (2) the weight values of $\omega\Ix{rec}$ and
$\omega\Ix{fb}$. Optimized parameters of type (1) are the
occupation probability $p$ for sparse random topologies (Erdös-Renyi
topology), the neighborhood range $k$ for ring topologies, and a ratio
parameter $q$ used to interpolate between Erdös-Renyi and ring
topologies. Optimized parameters of type (2) are the feedback strength
$\feedback\propto \omega\Ix{fb}$ and the gain value
$\gain\propto\omega\Ix{rec}$.

\paragraph{Fitness} The next step was to define the \emph{fitness} of
a given genotype when confronted with a range of different tasks, e.g.
waves of different frequencies. To express this formally, we introduce
\emph{challenges}: For a given seed value $\lambda$, the challenge $C$
yields a task $z' = C(\lambda)$. If we now apply a success function
$S(\mathcal{N}, z')\in\{0, 1\}$ that decides whether the network $\mathcal{N}$
has successfully reproduced the desired output $z'$, the fitness $F_C(G)$
of a genotype $G$ for $C$ may be defined as the expectation value of
$\lambda \mapsto S(G(\lambda), C(\lambda))$. For fixed challenges, the
main problem of optimizing the genotype thus is to find parameters
$\Theta$ that maximize $F_C$.

\section{Methods and Implementation}
\label{sec:implementation}

\paragraph{High and Low Frequency Challenges}
%For the optimization to work properly, the tasks presented to the networks
%must be chosen reasonably; they must be learnable by FORCE (at least in
%principle) and must be compatible with technical aspects like the
%integration time step.

Our concrete goal for this article was to examine which choice of genotype
parameters are optimal for learning sinusoidal waves with relatively high
or low frequencies. 
Based on preliminary simulation results we chose
$\nu\in[]$ as frequency range for the challenge $C\ix{high}$, producing
high frequency waves, and $\nu\in[]$ for $C\ix{low}$, producing low
frequency waves. 
Optimizing the fitness functions $F_{C\ix{high}}$ or $F_{C\ix{low}}$ thus
results in genotypes with the desired frequency properties.

%Based on our simulation results we found that can be expected to be
%learned using simple sinusoidal waves.
%We therefore used challenges $C\ix{high}$ and $C\ix{low}$ to specifically
%optimize genotypes for the high respectively low frequency region.

%To get a first estimate whether it might be possible to learn a given task
%using FORCE with 100 neurons in our network model, we looked at a single
%sinusoidal of frequency $\omega$ and determined the frequency range in
%which an (unoptimized) network (i.e. \gain, \feedback, \ERprob) is able to
%learn the function (see fig. \ref{}).

%Since we expect/hope that the optimized network extends this range of
%possible frequencies, we choose the frequencies for the optimization tasks
%from the slightly larger interval $[\num{0.6e-2}, 4]$ such that their logarithms
%are uniformly spaced. This allows for good resolution for both high and low
%frequencies.

\paragraph{Success}
To actually compute the fitness, we need a function $S$ that decides
whether a network succeeded to solve a task or not. To this end,
a measure $f(z', z)$ for the concordance of the target function $t\to z'(t)$ and
the network readout $t\to z(t)$ is sought. 
Though one could use a simple difference based metric, this has the
drawback that plain phase mismatches could produce high
differences for properly matching shapes.

%Though one could use a simple difference based metric, like the norm
%$f\ix{2}(z, z') = \left\|r-r'\right\|_2$, this has the drawback that small
%phase mismatches could produce high differences, even though the shape of
%$r$ matches the one of $r'$ well.

A measure that is time-shift independent and maximized for functions of
identical shape, on the contrary, is the maximum of the cross correlation 
\begin{align}
    f\ix{cor}(z, z') = \max_t \frac{\left<z, z'(\cdot
    - t)\right>}{\sqrt{\left< z, z\right> \left<z', z' \right>}}~.
\end{align}
Algorithmically, the signals $z$ and $z'$ are split into overlapping chunks
which are correlated separately.  This saves computational power and
prevents minute differences in frequency to accumulate into a huge phase
shift, so the phase only has to remain relatively constant over the
timescale of a single chunk (which is about 10 seconds of simulated time).
%This measure becomes problematic for functions that are very close to zero
%for a longer time (order of chunk size), but since we are going to work
%with superpositions of sinusoidals, this drawback
%is unproblematic.

Using this measure of quality, the success function for a network
$\mathcal{N}$ with readout $z$ for the task $z'$ was (by empirical means)
taken to be 
\begin{equation}
    S(\mathcal{N}, z') = \begin{cases} 1,\quad\mathrm{if}~f\ix{cor}(z, z') \ge 0.95,\\
                                       0,\quad\mathrm{if}~f\ix{cor}(z, z') < 0.95~.
                         \end{cases}
\end{equation}
%The threshold value of 0.95 was determined empirically, as signals $r$ with
%$f(z, z') \ge 0.95$ met our assessment of what we considered a good
%reproduction of the target pattern.

\paragraph{Genetic Optimization}
Due to the stochastic nature of a genotype $G$'s fitness $F_C(G)$,
a very high number of samples would be required to numerically obtain sufficiently
smooth approximations of $F_C(G)$ for typical optimization methods like
gradient descend or simulated annealing. But as the computational cost for
even one learning process is considerably high, these methods were not
feasible.

@@

Therefore, we optimized $F_C$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le M\right\}$
of $M$ individuals (Genotypes) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}[itemsep=1ex, leftmargin=0pt]
 \item[Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 50 samples (and adaptively more if the
     $(F_i)_{1\le i\le N}$ are spaced closely, to at most 100).
 \item[Selection] We choose $50\%$ of the most successful members of $G_t$ as survivors.
     With a small chance, a weaker generator can survive, in order to keep the gene pool more diverse.
\item[Reproduction] We then replace the $(1-p)|G_t|$ elements that did not make
    it into the next generation by either \emph{mutating} or \emph{recombining} the 
    survivors and get $\mathcal{G}_{t+1}$. This means we either change
    a single parameter randomly or take two individuals and randomly choose
    for each parameter from which parent to take the value.   
\end{description}

%\paragraph{Choice of Parameters and Algorithmic Quantities}
%The mutation rate of the parameters $\Theta$ of the genotypes\dots

@@

The most striking result is the strong growth of the feedback for
$C\ix{high}$ to values higher than 14, while the value for $C\ix{low}$
converges quickly to approximately 1 (FIG. \ref{fig:freq_optimization} (b)).
This behavior may indicate that the feedback pathway must
overshadow the (maybe too slow) internal mechanics for high frequencies,
while it is the other way round for low frequencies.
Indeed, FIG. \ref{fig:freq_optimization} (a) shows that genotypes with
a lower gain value (on average) are more successful for high frequencies,
which seems to fit in: excessive recurrent dynamics with a long time
scale (compared to the period to be learned) may disturb the learning.
%That the single genotypes remain quite scattered throughout the whole
%optimization process, though, implies that the exact gain value is not
%critical for the success of a genotype.

@@

But how well was the fitness actually improved during the optimization?
When looking at FIG. \ref{fig:freq_optimization} (d), one sees that the
fitness for $C\ix{high}$ increased during nearly the whole process, while
the algorithm failed to further optimize the genotypes' fitness for
$C\ix{low}$ after about 20 generations. A major reason for this is
probably, that the initial population for the $C\ix{low}$ optimization
already contained genotypes with parameters similar to the (at least
locally) optimal ones.

@@

\begin{figure}[hbct]
    {\footnotesize\input{pictures/top_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every Generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}

\section{Discussion}
%- Remarks
    %* Influence of initial conditions
        %-> Degenerated initial population poses major problems (does not
        %find same / takes very long to find same parameters as when started
        %with diversity).
        %-> With broad diversity: often fast convergence -> Gen. Optimizer
        %good as optimizing filter, but has hard times to explore new
        %parameter regions if no right genotypes are present (especially isolated
        %maxima of $F_C$). Solution: Could introduce migrants, that supply
        %the gene-pool with underrepresented genotypes.
    %* According to experience: maybe not ideal for finding single set of
      %parameters but rather for successful parameter-ranges (branches?)

%- Problems
    %* Only few and uncomprehensive number of test / experiments conducted due to the
      %computational cost.
    %* Influence of statistics: Learning success depends stronger on choice
      %of challenges than parameters (partially) -> must be very careful how to
      %interpret the results / should have used fixed array of challenges instead
      %of random sampling
